IOIs Analysis for Non-Expressive performances (OFFSET)

### 2020-04-02 material/analysis/ioi_offset.Rmd
checking IOI offsets
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'IOIs Analysis for Non-Expressive performances (ONSET)'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

```{r extract, include = FALSE}
df_ioi <- fread("./../preprocessor/filtered/data_onset.csv", header = T, sep = ",", dec = ".") # read a filtered csv

@@

```{r export, include = FALSE}
# export df_ioi
write.csv(df_ioi, file = "./data_ioi_onset.csv", row.names = F)
```

>>>>

---
title: 'IOIs Analysis for Non-Expressive performances (OFFSET)'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

```{r extract, include = FALSE}
df_ioi <- fread("./../preprocessor/filtered/data_offset.csv", header = T, sep = ",", dec = ".") # read a filtered csv

@@

```{r export, include = FALSE}
# export df_ioi
write.csv(df_ioi, file = "./data_ioi_offset.csv", row.names = F)
```
